A self-consistency check for unitary Hawking radiation

### 2016-10-31 Draft_BH_shells.tex
some more minor changes
punctuations, line/paragraph breaking in the appendix

A black hole of mass $M$ defines a Schwarzschild geometry for the spacetime with the following metric

\begin{equation}
	ds^2 = - \left( 1 -\frac{2M}{r} \right) dt^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{1}
\end{equation}

where we are working with units in which $G = c = 1$. We know there will be a flux of particles appearing from the horizon of the black hole \cite{Haw74}. Take some coordinate time interval, $\delta \bar{t_e}$, (which will have some corresponding proper time interval $\delta \bar{\tau_e}$) between two consecutive particles being emitted from the same position above the horizon of the black hole. An observer far away will see these particles arrive with some coordinate time interval $\delta \bar{t_0}$. We can follow the trajectory of the particles (assuming they are relativistic) from the position they are emitted, $r_e$, to the observer at $r_0$ by setting $ds = 0$ in Eq (\ref{1}). By confining the motion to be only in the radial direction, i.e $d \Omega_2 = 0$, we get the following geodesic equation

\begin{equation}
	\bar{t_e}^{(1)} - \bar{t_0}^{(1)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right)	\label{3}
\end{equation}

where the superscript represents particle $1$. An analogous geodesic equation is given for particle 2.

\begin{equation}
	\bar{t_e}^{(2)} - \bar{t_0}^{(2)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right).	\label{4}
\end{equation}

Since the right hand side of Eq (\ref{3}) and (\ref{4}) is the same, we see that

\begin{equation}
	\bar{t_0}^{(2)} - \bar{t_0}^{(1)} = \bar{t_e}^{(2)} - \bar{t_e}^{(1)} \Rightarrow \delta \bar{t_0} = \delta \bar{t_e}.
\end{equation}

Therefore the coordinate time interval when the particles are emitted remains the same when it is observed at distance $r_0$ as is shown in the bottom part of figure \ref{fig-setup}.

@@

Now we introduce two shells of matter with equal and opposite ADM mass, $\Delta M$ and $-\Delta M$ where $|\Delta M|<<M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig-setup}. We model these shells as infinitesimally thin and therefore use the Israel Junction Conditions (IJC) \cite{Isr66} with a delta function shell to analyze the effects of the shells. In this case the particle's move through two different spacetime regions. Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M+\Delta M$ as shown in the top part of figure \ref{fig-setup}.
\\
\\
As explained in the previous section, the proper time interval between two particles emitted at $r_e$, $\delta t_e$, is the same as the coordinate time interval at $r_1$, $\delta t_1$. Now we need to find the corresponding coordinate time interval in region $II$, $\delta \hat{t}_1$ (in general we will use hats on top of quantities that are evaluated in region $II$). To do this we simply note that the corresponding proper time at $r_1$, $\delta \tau_1$ must be the same in both regions of spacetime - this is a simple consequence of the IJC. The coordinate time intervals at $r_1$, in the two different regions, are therefore related by

>>>>

A black hole of mass $M$ defines a Schwarzschild geometry for the spacetime with the following metric,
\begin{equation}
	ds^2 = - \left( 1 -\frac{2M}{r} \right) dt^2 + \left( 1 - \frac{2M}{r} \right)^{-1} dr^2 + r^2 d \Omega_2^2	\label{1}~,
\end{equation}
where we are working with units in which $G = c = 1$. We know there will be a flux of particles appearing from the horizon of the black hole \cite{Haw74}. Take some coordinate time interval, $\delta \bar{t_e}$, (which will have some corresponding proper time interval $\delta \bar{\tau_e}$) between two consecutive particles being emitted from the same position above the horizon of the black hole. An observer far away will see these particles arrive with some coordinate time interval $\delta \bar{t_0}$. We can follow the trajectory of the particles (assuming they are relativistic) from the position they are emitted, $r_e$, to the observer at $r_0$ by setting $ds = 0$ in Eq (\ref{1}).

Confining the motion to be only in the radial direction, i.e $d \Omega_2 = 0$, we get the following geodesic equation,
\begin{equation}
	\bar{t_e}^{(1)} - \bar{t_0}^{(1)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right)~,	
	\label{3}
\end{equation}
where the superscript represents particle $1$. An analogous geodesic equation is given for particle 2. 
\begin{equation}
	\bar{t_e}^{(2)} - \bar{t_0}^{(2)} = \bar{r_0} - \bar{r_e} + 2M \ln \left( \frac{\bar{r_0} - 2M}{\bar{r_e} - 2M}  \right)~.	\label{4}
\end{equation}
Since the right hand side of Eq (\ref{3}) and (\ref{4}) is the same, we see that
\begin{equation}
	\bar{t_0}^{(2)} - \bar{t_0}^{(1)} = \bar{t_e}^{(2)} - \bar{t_e}^{(1)} \Rightarrow \delta \bar{t_0} = \delta \bar{t_e}~.
\end{equation}
Therefore the coordinate time interval when the particles are emitted remains the same when it is observed at distance $r_0$ as is shown in the bottom part of figure \ref{fig-setup}.

@@

Now we introduce two shells of matter with equal and opposite ADM mass, $\Delta M$ and $-\Delta M$ where $|\Delta M|<<M$, at a distance of $r_1$ and $r_2$ respectively as shown in the top part of figure \ref{fig-setup}. We model these shells as infinitesimally thin and therefore use the Israel Junction Conditions (IJC) \cite{Isr66} with a delta function shell to analyze the effects of the shells. In this case the particle's move through two different spacetime regions. Region $I$ is defined by the black hole of mass $M$ and region $II$ is defined by a Schwarzschild metric of mass $M+\Delta M$ as shown in the top part of figure \ref{fig-setup}.

As explained in the previous section, the proper time interval between two particles emitted at $r_e$, $\delta t_e$, is the same as the coordinate time interval at $r_1$, $\delta t_1$. Now we need to find the corresponding coordinate time interval in region $II$, $\delta \hat{t}_1$ (in general we will use hats on top of quantities that are evaluated in region $II$). To do this we simply note that the corresponding proper time at $r_1$, $\delta \tau_1$ must be the same in both regions of spacetime - this is a simple consequence of the IJC. The coordinate time intervals at $r_1$, in the two different regions, are therefore related by
